SIR Model With Testing Flows and Isolation

### 2020-11-05 codes/ali_test_sir.Rmd
fix parameter range W_s \neq W_I

```{r model inputs, message=FALSE}
params <- c(N0=1000000, beta=0.5,gamma=1/3, omega=0.25, rho=0.01, 
             W_S=1/3, W_I=1/3, W_R=1/3, #weights
             p_S=0, p_I=1, p_R=0.5, #prob of waiting for being tested positive
            eta_w=0.02, eta_t=0.01, #isolation parameter 
            s=2 #eta_w/eta_t
            )
class(params) <- "params_pansim"
state_init <- c(S_u=params[["N0"]], S_n=0,
                I_u=1,I_n=0,I_p=0,I_t=0,
                R_u=0,R_n=0,R_p=0,R_t=0,
                N=0,P=0)
d <- seq(0,200,by=0.1)
# Conditional stop for desolver
# rootfun <- function (time, state,params) { 
#   unpack(as.list(c(state,params)))
#   return(I_u - 1) }
```

>>>>

```{r model inputs, message=FALSE}
params <- c(N0=1000000, beta=.8,gamma=1/3, omega=0.25, rho=0.01, 
             W_S=0.5, W_I=1, W_R=1, #weights
             p_S=0, p_I=1, p_R=0.5, #prob of waiting for being tested positive
            eta_w=0.02, eta_t=0.01, #isolation parameter 
            s=2 #eta_w/eta_t
            )
class(params) <- "params_pansim"
state_init <- c(S_u=params[["N0"]], S_n=0,
                I_u=1,I_n=0,I_p=0,I_t=0,
                R_u=0,R_n=0,R_p=0,R_t=0,
                N=0,P=0)
d <- seq(0,200,by=0.1)
# Conditional stop for desolver
# rootfun <- function (time, state,params) { 
#   unpack(as.list(c(state,params)))
#   return(I_u - 1) }
```
